cvx-flats

### 2020-05-20 neurips-20/cvx-flats.tex
Adding my confusion on Lemma 5

\jessie{D $\implies$ A}
	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$, which is finite if $\Gamma$ is non-degenerate (i.e. there is no $p \in \simplex$ so that $\Gamma(p) = \emptyset$).
	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > 0$ (i.e. $\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.

	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
	Take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m);p) \to 0$.
	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.

\jessie{D $\implies$ C}
	Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
	Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
	Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
	As $u$ is in the space over which the surpremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
\end{proof}

>>>>

\jessie{$D \implies A$, but actually $\lnot B \implies \lnot D$}
Fix $p \in \simplex$.
Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.
This sequence converges to $0$, but we have $\lim_{m \to \infty} \zeta(\epsilon'_m) = \lim_{m \to \infty} \lim_{j \to \infty} \zeta(R_L(u^j_m, p)) \not \to 0$.

%commented out post meeting 05.20.2020
%\jessie{D $\implies$ B ($\iff$ A)}
%	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
%	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$, which is finite if $\Gamma$ is non-degenerate (i.e. there is no $p \in \simplex$ so that $\Gamma(p) = \emptyset$).
%	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > 0$ (i.e. $\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.
%	
%	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
%	Take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m);p) \to 0$.
%	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.
%		
\jessie{D $\implies$ C}
	Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
	Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
	Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
	As $u$ is in the space over which the surpremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
\end{proof}
